MSE Scenarios for short and long lived

### 2025-04-15 Scenarios.Rmd
Rec_sig that is

# Set sigma for NAA
# add higher rec_sig similar to redfish WHAM
rec_sig <- 1.0
NAA_sig <- 0.2
sigma_vals = array(NAA_sig, dim = c(n_stocks, n_regions, n_ages)) # n_stocks x n_regions x n_ages"
sigma_vals[,,1] = Rec_sig

>>>>

# Set sigma for NAA
# add higher rec_sig similar to redfish WHAM
Rec_sig <- 1.0
NAA_sig <- 0.2
sigma_vals = array(NAA_sig, dim = c(n_stocks, n_regions, n_ages)) # n_stocks x n_regions x n_ages"
sigma_vals[,,1] = Rec_sig
